### 2016-11-13 Paper_v6.tex
Added supplementary figures

>>>>

\begin{figure}[ht]
\centering
\includegraphics[clip, trim=0.5cm 7cm 0.5cm 1.80cm, width=1.00\textwidth]{./figs/Figure_S4.pdf}
\caption{ Convergence curves for different metaheuristics along with CMA-ES) Objective function value versus the number of function evaluations for \textbf {(A)} Ackley 300 dimensional \textbf {(B)} and Rastrigin 300 dimensional.
}\label{fig-CMA-ES convergences}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./figs/Figure_S5.pdf}
\caption{ (Convergence curves for eSS and DOPS) Objective function value versus the number of function evaluations plotted for eSS and DOPS on \textbf {(A)} Coagulation \textbf {(B)} CHO Model \textbf {(C)} Ackley 300 dimensional and \textbf {(D)} Rastrigin 300 dimensional.
}\label{fig-convergence eSS}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./figs/Figure_S6.pdf}
\caption{ (Dispersion curves for DOPS) Objective function value (25 trials) versus the number of function evaluations plotted for DOPS on \textbf {(A)} Ackley 300 dimensional \textbf {(B)} Rastrigin 300 dimensional \textbf {(C)}CHO Model - B4 \textbf {(D)} Coagulation. For CHO Model and Coagulation Y-axis is in log scale.
}\label{fig-dispersion}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./figs/Figure_S7.pdf}
\caption{ Fig. S7: (Variability analysis for best objective value): Boxplots for different metaheuristics on \textbf {(A)} Ackley 300 dimensional \textbf {(B)} Rastrigin 300 dimensional \textbf {(C)} CHO Model - B4 \textbf {(D)} and Coagulation
}\label{fig-boxplot}
\end{figure}
